% Privacy Policy Template for Blockchain Startup

\documentclass[12pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{enumitem}

% Page layout
\geometry{a4paper, margin=1in}
\setlength{\headheight}{15pt}
\setstretch{1.3}

% Header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Privacy Policy}
\fancyhead[R]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{Privacy Policy}}\\[0.5cm]
    {\large [COMPANY NAME]}\\[0.2cm]
    {\large Last Updated: [DATE]}
\end{center}

\section{Introduction}

At [COMPANY NAME] ("we," "us," or "our"), we respect your privacy and are committed to protecting your personal information. This Privacy Policy explains how we collect, use, disclose, and safeguard your information when you use our blockchain-based [SERVICE/PLATFORM/APPLICATION] (the "Service").

Please read this Privacy Policy carefully. By accessing or using our Service, you acknowledge that you have read, understood, and agree to be bound by all the terms of this Privacy Policy.

\section{Information We Collect}

\subsection{Information You Provide}

We may collect personal information that you voluntarily provide when using our Service, including:

\begin{itemize}
    \item Contact information (email address, phone number)
    \item Account credentials
    \item KYC/AML information (if applicable)
    \item Wallet addresses
    \item Correspondence you send to us
\end{itemize}

\subsection{Information Collected Automatically}

When you use our Service, we may automatically collect certain information, including:

\begin{itemize}
    \item Technical data (IP address, browser type, device information)
    \item Usage data (interactions with our Service)
    \item Blockchain transaction data
    \item Cookies and similar tracking technologies
\end{itemize}

\subsection{On-Chain vs. Off-Chain Data}

Our Service involves both on-chain and off-chain data:

\textbf{On-chain data} includes information recorded on the blockchain, which is publicly visible and immutable by nature. This may include:
\begin{itemize}
    \item Wallet addresses
    \item Transaction amounts
    \item Smart contract interactions
    \item Timestamps
\end{itemize}

\textbf{Off-chain data} is stored in our conventional systems and includes:
\begin{itemize}
    \item Contact information
    \item KYC/AML information
    \item User preferences
    \item Account details
\end{itemize}

\section{How We Use Your Information}

We may use the information we collect for various purposes, including to:

\begin{itemize}
    \item Provide, maintain, and improve our Service
    \item Process transactions and execute smart contracts
    \item Verify your identity and prevent fraud
    \item Comply with legal obligations, including KYC/AML requirements
    \item Send you technical notices and support messages
    \item Communicate with you about products, services, and events
    \item Monitor and analyze usage patterns and trends
\end{itemize}

\section{Blockchain Data and Privacy}

\subsection{Public Nature of Blockchain}
All transactions conducted on the blockchain are public and transparent. While blockchain addresses themselves are pseudonymous, it may be possible for third parties to analyze the blockchain and associate your activities with your identity.

\subsection{Immutability}
Due to the immutable nature of blockchain technology, once data is recorded on-chain, it cannot be altered or deleted. This includes transaction data linked to your wallet address.

\subsection{Smart Contracts}
When you interact with smart contracts through our Service, these interactions are recorded on the blockchain and cannot be removed.

\section{Data Sharing and Disclosure}

We may share your information with:

\begin{itemize}
    \item Service providers and business partners who help us deliver our Service
    \item Legal and regulatory authorities, when required by law
    \item Other users, for certain features where user interaction is necessary
    \item In connection with a business transaction (merger, acquisition, sale of assets)
    \item With your consent or at your direction
\end{itemize}

\section{Security Measures}

We implement reasonable security measures to protect your personal information from unauthorized access, alteration, disclosure, or destruction. However, no internet or blockchain transmission is completely secure, and we cannot guarantee the security of your information.

For off-chain data, we employ industry-standard security protocols. For on-chain data, we recommend users take additional security precautions, such as:

\begin{itemize}
    \item Using hardware wallets when possible
    \item Maintaining private key security
    \item Being cautious about sharing wallet addresses publicly
\end{itemize}

\section{User Rights and Choices}

Depending on your location, you may have certain rights regarding your personal information:

\begin{itemize}
    \item Access and review personal information we hold about you
    \item Request correction of inaccurate information
    \item Request deletion of off-chain data (subject to legal obligations)
    \item Opt-out of certain data collection or marketing communications
    \item Data portability
\end{itemize}

\textbf{Note on Blockchain Data:} Due to the immutable nature of blockchain technology, we cannot delete or modify any data recorded on-chain, including transaction history associated with your wallet address.

\section{Retention of Information}

We retain your personal information for as long as necessary to fulfill the purposes outlined in this Privacy Policy, unless a longer retention period is required or permitted by law. On-chain data will remain on the blockchain indefinitely.

\section{Children's Privacy}

Our Service is not intended for individuals under the age of 18. We do not knowingly collect personal information from children. If you believe we have inadvertently collected information from a child, please contact us immediately.

\section{International Data Transfers}

Your information may be transferred to and processed in countries other than your country of residence. These countries may have different data protection laws. We will take appropriate measures to protect your information in accordance with this Privacy Policy.

\section{Changes to this Privacy Policy}

We may update this Privacy Policy from time to time. The updated version will be indicated by an updated "Last Updated" date. We encourage you to review this Privacy Policy periodically.

\section{Contact Us}

If you have questions or concerns about this Privacy Policy or our data practices, please contact us at:

\begin{itemize}
    \item Email: [CONTACT EMAIL]
    \item Address: [COMPANY ADDRESS]
\end{itemize}

\section{Legal Basis for Processing (for EEA, UK, and Similar Jurisdictions)}

For users in the European Economic Area (EEA), United Kingdom, and similar jurisdictions, we process your personal information based on one or more of the following legal bases:

\begin{itemize}
    \item Performance of a contract
    \item Legitimate interests
    \item Compliance with legal obligations
    \item Your consent
\end{itemize}

\section{Additional Information for Specific Jurisdictions}

\subsection{California Residents}

California residents may have additional rights under the California Consumer Privacy Act (CCPA) and other state laws.

\subsection{EU/EEA Residents}

Residents of the European Union and European Economic Area have specific rights under the General Data Protection Regulation (GDPR).

    [ADD JURISDICTION-SPECIFIC INFORMATION AS NEEDED]

\section{Cookies and Tracking Technologies}

We and our third-party service providers use cookies and similar tracking technologies to track activity on our Service. You can instruct your browser to refuse all cookies or to indicate when a cookie is being sent.

\section{DeFi and Web3-Specific Provisions}

\subsection{Non-Custodial Services}
If our Service operates in a non-custodial manner, we do not control or have access to your private keys or funds. You are solely responsible for securing your private keys.

\subsection{Decentralized Protocols}
When you interact with decentralized protocols through our Service, you may be subject to additional terms and privacy policies of those protocols, which we do not control.

\subsection{Airdrops and Rewards}
If we conduct airdrops, distribute rewards, or provide incentives, we may use wallet addresses and on-chain activity to determine eligibility.

\end{document}